%-------------------------
% Resume in Latex
% Author : Bhavi Shah
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.6in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-4pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
       \textbf{#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------


\begin{center}
    \textbf{\Huge \scshape Bhavi Shah} \\ \vspace{1pt}
    \small 312-358-6415 $|$ \href{mailto:bhavi1711999@gmail.com }{\underline{bhavi1711999@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/bhavi--shah/}{\underline{linkedin.com/in/bhavi-shah}} $|$
    \href{https://github.com/bhavi-shah}{\underline{github.com/bhavi-shah}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Illinois Institute of Technology }{Chicago, IL}
      {Master of Data Science \textbf{}}{January 2021 - Present}
          \resumeItemListStart
            \resumeItem{Top Courses: Data Preparation and Analysis, Applied Statistics, Project Management, Machine Learning, Statistical Learning, Big Data Technologies, Data Mining  }
        \resumeItemListEnd
  \resumeSubHeadingListEnd
  
%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, SQL, R, Java} \\
     \textbf{Databases}{: SQL Server, MySQL, Snowflake, MongoDB, Oracle} \\
     \textbf{Tools}{: SSIS, SSAS, Power BI, Tableau,Microsoft SQL Server Management, Hadoop, Hive, HBase } \\
     \textbf{Cloud Services}{: Amazon Web Services, Microsoft Azure, Google Cloud Platform} \\
      \textbf{Python Libraries}{: Pandas, NumPy, Scikit-learn, Matplotlib, Pytorch, Keras, TensorFlow} \\
     
    }}
 \end{itemize}


%-------------------------------------------

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Data Scientist}{January 2022 - May 2022}
      {CCC Intelligent Solutions Inc.}{Chicago, IL}
      \resumeItemListStart
        \resumeItem{Developed and deployed a project of \textbf{Machine} \textbf{Unlearning} under my Data Science Practicum Training with a team of 5 members using \textbf{Python} technology. }
        \resumeItem{Deployed the model to evaluate the possibility of unlearning the impact of small set of the original dataset used to train the model.}
        \resumeItem{Experience in the following areas: machine learning, recommendation systems, pattern recognition, large-scale data mining and artificial intelligence.}
        \resumeItem{Implemented the framework of \textbf{SISA} training to expediate the learning process and improve the performance with reduction in computational overhead associated with unlearning.}
         
      \resumeItemListEnd
      
    \resumeSubheading
      {Data Scientist Intern}{December 2019 - September 2020}
      {Digimation Technologies Pvt. Ltd}{Ahmedabad, India}
      \resumeItemListStart
        \resumeItem{Worked with \textbf{Pandas/Numpy} to analyze the data and developed dashboards and reports on \textbf{Tableau} to help business team to make data driven decision.}
        \resumeItem{Used \textbf{SQL} for the DB and various python libraries for data analysis and predictive modeling. }
        \resumeItem{Implemented \textbf{ETL pipeline} from OLTP databases to OLAP data warehouse, ensured data completeness, accuracy, and consistency.}
        \resumeItem{Used \textbf{Python} to create regression models, clustering algorithm and other data mining methods to explore the fast growth opportunities of the clients.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Data Analyst Intern}{May 2019 - November 2019}
      {AIS Technolabs Pvt. Ltd.}{Ahmedabad, India}
      \resumeItemListStart
        \resumeItem{Worked with business owners to identify key data elements monitored on an on-going basis to ensure a high level of data quality within the Warehouse. Followed \textbf{Agile Methodology} and adherence to the \textbf{Scrum Methodology}.}
        \resumeItem{Extract, transform, cleanse, and load (\textbf{ETL}) data into Microsoft SQL Server, Staging Databases using \textbf{SSIS}.}
        \resumeItem{Wrote \textbf{SQL} scripts and queries to extract data from various data sources and for daily testing.}
        \resumeItem{Developed reports to the specification of Business Intelligence group by using \textbf{Tableau Desktop}.}
        
      \resumeItemListEnd
      
    \resumeSubHeadingListEnd
    

%-----------PROJECTS New-----------
\section{Projects}
  \resumeSubHeadingListStart
     \resumeProjectHeading
      {Snowflake Data Warehouse}{Snowflake, SQL, Python, Power BI, SSIS, AWS}
      \resumeItemListStart
        \resumeItem{Created Data Warehouse model to direct aspects such as sourcing, transformation, and extraction.}
        \resumeItem{ Performed Data Migration from BAAN database to \textbf{Snowflake.}}
        \resumeItem{Automated ETL processes using \textbf{Prefect} (Python), making it easier to wrangle data \& reducing the time by 40\%.}
        \resumeItem{Devised reports and visualizations to present requested data in a sleek format using \textbf{Power BI} dashboard.}
      \resumeItemListEnd
      
     \resumeProjectHeading
      {Yelp Data Analysis}{Hive, Pig, Python, Data Mining, EDA}
      \resumeItemListStart
        \resumeItem{Analyzed Yelp datasets to help restaurants get better ratings and related suggestions to make more business.}
        \resumeItem{ The project tracks down data about organizations across 11 metropolitan areas in the nation using \textbf{Hive} and \textbf{Pig} to get insights that which factors of restaurants matters more to the customers and which aspects can be ignored which helps in finding trusted reviewers.}
      \resumeItemListEnd
      
     \resumeProjectHeading
      {Image Segmentation using Mask R-CNN}{Python, Neural Networks, Computer Vision, K-Means}
      \resumeItemListStart
        \resumeItem{Created an Image segmentation model using \textbf{Mask R-CNN} model based on Feature Pyramid Network and Resnet-101 to extract features from the images on the COCO dataset.}
        \resumeItem{ Improved the speed and efficiency for object detection and achieved 94\% accuracy in generating masks and identifying objects in the dataset.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
\end{document}
